\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{casual} % Thèmes existant : empty, classirc, casual, banking; Couleurs du thème existant : blue, orange, green, red, purple, grey, black
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{hscale=0.80,vscale=0.80,centering}

\firstname{Thibault}
\familyname{MILLANT}
\title{09/02/1992 - Student in Engineering School}
\address{34 Boulevard Cointet}{06400 Cannes}
\email{tmillant@gmail.com}
\mobile{+1 617 337 7116}
\phone{+33 4 93 48 88 46}
\extrainfo{Twitter @MThibault06}
\extrainfo{Driving licence}
%\photo{photo.jpg} % Pas sur les CV anglais

\begin{document}
\maketitle
\section{Experience} % partie Compétences
\cventry{May 2014-Today}{Internship Data Analyst \& Software Developer}{Amadeus Boston}{USA}{}{Internship in  R\&D, division AIR and SSP (Searching, Shopping, and Pricing). Data Analyst. Softawre engineer for statistics tools. Bugs and errors reporting.}
\cventry{January 2014 - Today}{Assisting Teacher in computer tutorials}{ECE Paris}{}{}{}
\cventry{July 2011 - Today}{Computer tutoring}{Freelance}{}{}{Private computing instructor for all levels and on all operating systems : teaching, installations, rescues...}
\cventry{Oct 2014 - April 2015}{Internship/Personal Project}{National Assembly}{}{}{Safety study of the National Assembly's IT infrastucture, according to the ANSSI guide of IT hygiene and the PSSIE. Drafting of newsletters about best practices concerning IT security aimed at members of parliament and staff.} 
\cventry{June 2014 - August 2014}{Internship}{SCM Centre d'Imagerie Médicale Belvédère}{}{}{Website set up, IOS application set up, self-hosting work, and staff training.}
\cventry{June 2013 - July 2013}{Internship}{Schneider-Electrique Carros}{}{}{Internship in IT security on PLC. French and English technical report for Schneider-Electric.}
\cventry{April 2014 - April 2015}{Treasurer and System Administrator}{iTeam}{}{}{Association of promotion of Open-Source software and the IT security.}
\cventry{Sept. 2012 - Today}{Vice-President}{Équipe Système}{}{}{Computing association to help and assist students. We act in collaboration with  system administrators.}
\cventry{Sept. 2012 - May 2013}{Microsoft Ambassador}{Microsoft France}{}{}{Microsoft representative on my campus, demonstration of products, training.}
\cventry{Nov. 2011 - Today}{Administrator}{Freedom-IP}{}{}{Administrator of a VPN community and its forum.}
\cventry{Oct. 2013 - Dec 2014}{Administrator}{Journal du Pirate}{}{}{Managing the forum. Assistance and maintenance of the forum.}
\cventry{Nov. 2011 - Oct. 2013}{Moderator}{Journal du Pirate}{}{}{Moderator of the forum. Assistance and maintenance of the forum.}

\section{IT Skills} % partie Compétences
\cvitem{}{\textbf{Programmation}}
\cvitem{Web}{HTML5, CSS3, PHP5, JS, Twitter bootstrap, CakePHP}
\cvitem{Software}{C, C++, Java, Python}
\cvitem{Graphics Libraries}{GTK, Allegro}
\cvitem{Database}{Microsoft Access, MySQL}
\cvitem{Others}{Bash, \LaTeX}
\cvitem{Electronics}{VHDL} % liste d'items

\cvitem{}{\textbf{Operating System}} % une double liste
\cvitem{}{Debian and its derivatives (Ubuntu, KaliLinux, etc...), Archlinux, Windows (95 - 8.1), Macintosh}
\cvitem{}{}

\cvitem{}{\textbf{Softwares}} % une double liste
\cvitem{Virtualization}{VirtualBox, VMWare}
\cvitem{Office Automation}{LibreOffice, Microsoft Office 2003, 2007, 2010, 2013, 365} % une double liste
\cvitem{IDE}{Codeblocks, Eclipse, NetBeans, PHPStorm} % une double liste
\cvitem{Remote Access}{SSH, VNC, Teamviewer} % une double liste
\cvitem{Electronics}{PSpice/Schematics, Xilinx} % une double liste
\cvitem{Mathematics}{MatLab} % liste d'items

\section{Education} % Partie Formations
\cventry{2012-Today}{Engineering School}{Paris}{Information Systems Department}{Personal Project}{\textbf{\textit{ECE Paris}}} % ligne du diplôme
\cventry{Sept 2013 - Dec 2013}{Exchange Semester in Computer Science}{Montreal}{Canada}{}{\textbf{\textit{Concordia University}}}
\cventry{2010-2011}{Faculty of Medecine}{Nice}{France}{}{\textbf{\textit{University of Nice-Sophia Antipolis}}}
\cventry{1995-2010}{Italian European Baccalaureate, with distinction}{Cannes}{France}{}{\textbf{\textit{Institut Stanislas}}}

\section{Languages} % partie Compétences
\cventry{}{French}{Mother tongue}{}{}{}
\cventry{}{English}{Intermediary}{TOEIC : 805}{IELTS : 7.5/9}{}
\cventry{}{Italian}{Intermediary}{}{}{}
\cvitem{}{}

\section{Interests}
\cventry{}{Computing}{Linux (Association of promotion of Open-Source software and the IT security : iTeam), Network, Server, Security, Virology, Cryptography, security-oriented challenges (Position : 1470 / 39413)}{}{}{}
\cventry{}{New Technologies}{Raspberry Pi, Information Systems, VPN}{}{}{}
\cventry{}{Sports}{Snowboard and Ski (Competition), Funboard, Wakeboard, Surf, Tennis (Competition)}{}{}{}
\cventry{}{Music}{Piano and Guitare for 8 ans}{}{}{}

\end{document}
